A Topic Model of Climate Change Literature

### 2019-04-24 tables/growth_table.tex
nmf

\begin{tabular}{l p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}} 
&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &625 & 7623 & 16395 & 34510 & 117758 & 128266\\ 
\textbf{Words} &1380 & 12409 & 20453 & 32644 & 67064 & 74196\\ 
\textbf{New words} & change (296) & loss (552) & downscaling (197) & sres (217) & biochar (1752) & mmms (192)\\ & climate (262) & efficiency (515) & degreesc (145) & petm (95) & redd (1058) & c3n4 (132)\\ & model (168) & mol (439) & ncep (130) & amf (87) & cmip5 (656) & cop21 (107)\\ & effect (160) & ambient (417) & otcs (87) & sf5cf3 (81) & cmip3 (569) & cmip6 (104)\\ & co2 (156) & coal (404) & nee (87) & cwd (74) & wrf (334) & zika (75)\\ & atmospheric (152) & photosynthetic (393) & fco (80) & embankment (72) & mofs (288) & brgdgts (71)\\ & climatic (133) & concern (381) & hadcm2 (78) & aod (69) & sdm (283) & twitter (68)\\ & global (131) & chamber (353) & dtr (75) & clc (69) & gosat (281) & jing (66)
\end{tabular}

>>>>

\begin{tabular}{l p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}} 
&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &1167 & 8539 & 21716 & 38750 & 134413 & 201606\\ 
\textbf{Words} &2000 & 12480 & 23346 & 34637 & 71867 & 94746\\ 
\textbf{New words} & change (560) & oil (287) & downscaling (217) & sres (234) & biochar (1791) & mmms (313)\\ & climate (428) & deltac (283) & degreesc (187) & petm (95) & redd (1113) & cop21 (234)\\ & co2 (318) & whole (256) & ncep (130) & amf (88) & cmip5 (679) & c3n4 (214)\\ & climatic (289) & tax (254) & fco (107) & sf5cf3 (86) & cmip3 (587) & sdg (187)\\ & model (288) & landscape (249) & pfc (98) & clc (81) & mofs (299) & zika (182)\\ & atmospheric (281) & alternative (243) & otcs (98) & embankment (81) & sdm (297) & ndcs (168)\\ & effect (280) & availability (242) & dtr (95) & cwd (79) & mof (275) & indc (164)\\ & global (224) & life (239) & nee (89) & etm (75) & biochars (252) & indcs (134)
\end{tabular}
